|

### 2022-12-27 paper.Rmd
Tue Dec 27 03:05:17 CET 2022: update-remote.sh

````{python3}
import json

S = json.load(open("./data/airfoil_FullRun_30gens/MWU-BestFitnessByGen.json", "r", encoding="utf-8"))
statistic_mwu_fitness = S["statistic"]
pval_mwu_fitness = S["p-value"]

print(pval_mwu_fitness)
````

>>>>

```{python include=FALSE}
import json

S = json.load(open("./data/airfoil_FullRun_30gens/MWU-BestFitnessByGen.json", "r", encoding="utf-8"))
statistic_mwu_fitness = S["statistic"]
pval_mwu_fitness = round(S["p-value"], 4)

````
The result of the MWU test is `r py$pval_mwu_fitness`!
